### 2020-07-20 paper/methods.tex
After Andrei's comments

The Chinese Academy of Sciences started the program of Thorium Molten Salt Reactor (TMSR) in 2011 \cite{jiang2012advanced}, and many works have been done on the design of MSR and the use of Thorium with the Th-U fuel cycle \cite{li_optimization_2018,li2015analysis}. Among them, the SD-TMSR is proposed in 2018 \cite{li_optimization_2018}, which is a graphite-moderated molten salt reactor with thermal power of 2,250 MW$_{th}$. The design of the SD-TMSR is inspired by the \gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential}, which combines the advantages of high breeding ratio (BR) in fast spectrum and low fissile inventory of $^{233}$U in thermal spectrum. The negative temperature coefficient of reactivity is also achieved in the design of SD-TMSR. Figure~\ref{fig:ff} illustrates the quarter-core view of the 
SD-TMSR. The core of the 
SD-TMSR is a right cylinder divided into an inner zone (486 fuel tubes) 
and an outer zone (522 fuel tubes) to enhance breeding performance.
\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
		SD-TMSR \cite{ashraf2019Preliminary}.}
	\label{fig:ff}
\end{figure}
In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
where HM is the heavy metal (i.e. $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the 
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the channels
that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the SD-TMSR pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the SD-TMSR are 
summarized in Table~\ref{tab:table1}.

>>>>

The Chinese Academy of Sciences started the program of Thorium Molten Salt Reactor (TMSR) in 2011 \cite{jiang2012advanced}, and many works have been done on the design of MSR and the use of Thorium with the Th-U fuel cycle \cite{li_optimization_2018,li2015analysis}. Among them, the SD-TMSR is proposed in 2018 \cite{li_optimization_2018}, which is a graphite-moderated molten salt reactor with thermal power of 2,250 MW$_{th}$. The design of the SD-TMSR is inspired by the \gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential}, which combines the advantages of high breeding ratio (BR) in fast spectrum and low fissile inventory of $^{233}$U in thermal spectrum. The negative temperature coefficient of reactivity is also achieved in the design of SD-TMSR. Figure~\ref{fig:ff} illustrates the quarter-core view of the 
SD-TMSR. The core of the 
SD-TMSR is a right cylinder divided into an inner zone (486 fuel tubes) 
and an outer zone (522 fuel tubes) to enhance breeding performance.
\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
		SD-TMSR \cite{ashraf2019Preliminary}.}
	\label{fig:ff}
\end{figure}
In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
where HM is the heavy metal (i.e., $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the 
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the channels
that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the SD-TMSR pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the SD-TMSR are 
summarized in Table~\ref{tab:table1}.

### 2020-07-20 paper/results.tex
After Andrei's comments

The control rod parameters including control rod worth (CRW), interference 
between CR clusters, and integral and differential control rod worths are 
described in this part. Table~\ref{tab:worth} shows calculated CRW and the amplification 
factor (A$_{CRi}$) for six different 
absorbers. The types of interference for all different 
absorbers are listed in Table ~\ref{tab:table25}. Fuel salt composition of LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ at 70-17.5-12.3-0.2 mole\% is used to generate the results listed in Tables~\ref{tab:worth} and ~\ref{tab:table25}.
\begin{sidewaystable}
	\fontsize{5}{7}\selectfont
	\centering
	\caption{The control rod worth for different CR 
		materials.}
	\vspace{1ex}
	\begin{tabularx}{\textwidth}{|p{1.8cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}| 
			p{1cm}|p{1cm}|p{1cm}|p{1cm}| 
			p{1cm}|p{1cm}|p{1cm}|p{0.9cm}|}
		\hline
		\multirow{2}{*}{Control Rod group}		& 
		\multicolumn{2}{c|}{Nat. B$_4$C} & \multicolumn{2}{c|}{B$_4$C-90}   	&\multicolumn{2}{c|}{HfB$_2$}	
		&\multicolumn{2}{c|}{HfH$_{1.62}$} 
		&\multicolumn{2}{c|}{Gd$_2$O$_3$}	& 	
		\multicolumn{2}{c|}{Eu$_2$O$_3$} \\
		\cline{2-13}
		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	
		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$		
		&$\Delta\rho$$_{CRi}$ [\$]  &A$_{CRi}$		
		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$		
		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$		
		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$  \\
		\hline                   
		All control rods      &  $42.04\pm0.60$	&	& $48.19\pm0.68$   &		
		&$40.40\pm0.41$	&		&$37.96\pm0.36$	&		&$33.70\pm0.40$	&	
			&$42.39\pm0.48$	& 	 \\
		\hline 
		CSD 		 & $22.32\pm0.20$ 	& $1.24\pm0.01$	 			& $25.50\pm0.23$   &$1.24\pm0.01$	 	&$21.90\pm0.17$	&$1.10\pm0.01$	 	&$20.62\pm0.34$	&$1.10\pm0.01$	 	&$18.48\pm0.25$	&$1.17\pm0.01$	 	&$22.96\pm0.18$	&$1.20\pm0.01$   \\
		\hline 
		SSD		   & $14.27\pm0.10$ 	&$1.38\pm0.02$	 	&$16.39\pm0.11$ &$1.38\pm0.02$	 	&$14.27\pm0.21$	&$1.29\pm0.01$	 	&$13.23\pm0.18$	&$1.30\pm0.06$	 	&$12.00\pm0.20$	&$1.26\pm0.01$	 	&$14.58\pm0.11$	&$1.30\pm0.02$	  \\
		\hline 
		CSD inner ring   &  $16.80\pm0.02$	&$1.50\pm0.01$	  &  $18.42\pm0.05$  &$1.60\pm0.04$	 		&$16.29\pm0.29$	&$1.48\pm0.02$	 	&$15.50\pm0.17$	& $1.46\pm0.01$  	&$14.12\pm0.07$	&$1.39\pm0.01$	 	&$16.92\pm0.13$	&$1.50\pm0.01$	  \\
		\hline 
		CSD outer ring            &  $2.16\pm0.02$	&$3.11\pm0.06$	     &$2.26\pm0.02$ &$4.21\pm0.07$	 	&$2.10\pm0.06$	&$3.11\pm0.10$ 	&$1.85\pm0.07$	&$3.24\pm0.06$	 	&$1.80\pm0.10$	&$2.54\pm0.14$	 	&$2.14\pm0.05$	&$3.20\pm0.05$	  	\\
		\hline 
		CSD2			 &  $2.11\pm0.03$	&$3.00\pm0.08$	 			& $2.25\pm0.04$   &$3.69\pm0.16$	 	&$2.24\pm0.05$	&$2.42\pm0.10$	 	&$2.00\pm0.10$	&$2.68\pm0.03$	 	&$1.80\pm0.10$	&$2.55\pm0.20$	 	&$2.19\pm0.12$	&$2.90\pm0.08$	  \\
		\hline 
		CSD9			 &  $0.06\pm0.01$	&$15.16\pm0.10$	 				& $0.15\pm0.04$   & $10.53\pm0.01$	  	&$0.10\pm0.05$	&$5.10\pm0.05$	 	&$0.05\pm0.01$	&$16.40\pm0.10$	  	&$0.09\pm0.07$	&$5.55\pm0.20$	  	&$0.07\pm0.05$	&$14.00\pm0.10$	  \\ 
		\hline
		SSD1		 &  $3.95\pm0.05$	&$1.31\pm0.01$	 	& $4.18\pm0.07$   &$1.59\pm0.08$	 	&$3.95\pm0.13$	&$1.30\pm0.07$	 	&$3.59\pm0.03$	&$1.49\pm0.01$	 	&$3.45\pm0.12$	&$1.40\pm0.08$	 	&$3.91\pm0.06$	&$1.40\pm0.01$  \\
		\hline 
		SSD4		 &  $0.59\pm0.08$	& $9.52\pm0.10$	 		&  $0.57\pm0.09$  &$7.84\pm0.15$	 	&$0.63\pm0.06$	&$4.40\pm0.10$	 	&$1.00\pm0.05$	&$2.51\pm0.16$	 	&$0.60\pm0.80$	&$3.31\pm0.27$	 	&$0.60\pm0.08$	&$5.10\pm0.28$	  \\
		\hline
	\end{tabularx}
	\label{tab:worth}
\end{sidewaystable}

@@

Among the absorbers investigated, the total worth of all CRs extends from $33.7\pm0.4$ $\$$ to $48.19\pm0.68$ 
$\$$ (the first row in Table~\ref{tab:worth}). B$_4$C-90 (boron enriched to 90\% $^{10}$B)
has the largest absorption ability, while Gd$_2$O$_3$ has the lowest 
absorption compared with the other absorbing materials in this study. This 
result agrees with macroscopic absorption cross section data 
\cite{guo2019optimized}. B$_4$C-90 has the highest macroscopic 
absorption cross section followed by Eu$_2$O$_3$, natural B$_4$C (Nat. B$_4$C), HfB$_2$, HfH$_{1.62}$, and 
finally Gd$_2$O$_3$. The CR material is being transmuted during 
operation; the effect of the fuel salt burnup on the CRW is neglected
herein and will be investigated and presented in Part II of this 
study.

@@

We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters (i.e. clusters located in the center and at the boundary between the core
zones, see Figure~\ref{fig:core_25}) to investigate the variation of CRW with the position in the inner core.
The CRW decreases in the direction of the outer core zone. The outer core zone 
has smaller moderator-to-fuel ratio ($0.86$) compared with the central zone 
($2.8$); consequently, the neutron energy spectrum is faster in the peripheral 
zone than in the center of the core degrading the CR's 
absorption ability in that region.

@@

The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner 
ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The 
anti-shadowing is observed when the combined rod worth is greater than the sum 
of the individual worths. As listed in Tables~\ref{tab:worth} and ~\ref{tab:table25}, the strongest anti-shadowing effect occurred in 
SSD4 and CSD9 clusters that are located at the boundary between the core zones 
with different moderator-to-fuel ratios. This can be attributed to the fact that the SSD4 and CSD9 clusters are surrounded by fewer clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~\ref{fig:core_25}). Consequently, low interference between the SSD4 and CSD9 clusters and other surrounding clusters is observed. The obtained results show a negligible relationship between the absorbing material type and the interference between the CR clusters (i.e. the A$_{CRi}$).

>>>>

The control rod parameters including control rod worth (CRW), interference 
between CR clusters, and integral and differential control rod worths are 
described in this work. Table~\ref{tab:worth} shows calculated CRW and the amplification 
factor (A$_{CRi}$) for six different 
absorbers. The types of interference for all different 
absorbers are listed in Table ~\ref{tab:table25}. Fuel salt composition of LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ at 70-17.5-12.3-0.2 mole\% is used to generate the results listed in Tables~\ref{tab:worth} and ~\ref{tab:table25}.
\begin{sidewaystable}
	\fontsize{5}{7}\selectfont
	\centering
	\caption{The control rod worth for different CR 
		materials.}
	\vspace{1ex}
	\begin{tabularx}{\textwidth}{|p{1.8cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}| 
			p{1cm}|p{1cm}|p{1cm}|p{1cm}| 
			p{1cm}|p{1cm}|p{1cm}|p{0.9cm}|}
		\hline
		\multirow{2}{*}{Control Rod group}		& 
		\multicolumn{2}{c|}{Nat. B$_4$C} & \multicolumn{2}{c|}{B$_4$C-90}   	&\multicolumn{2}{c|}{HfB$_2$}	
		&\multicolumn{2}{c|}{HfH$_{1.62}$} 
		&\multicolumn{2}{c|}{Gd$_2$O$_3$}	& 	
		\multicolumn{2}{c|}{Eu$_2$O$_3$} \\
		\cline{2-13}
		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	
		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$		
		&$\Delta\rho$$_{CRi}$ [\$]  &A$_{CRi}$		
		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$		
		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$		
		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$  \\
		\hline                   
		All control rods      &  $42.04\pm0.60$	&	& $48.19\pm0.68$   &		
		&$40.40\pm0.41$	&		&$37.96\pm0.36$	&		&$33.70\pm0.40$	&	
			&$42.39\pm0.48$	& 	 \\
		\hline 
		CSD 		 & $22.32\pm0.20$ 	& $1.24\pm0.01$	 			& $25.50\pm0.23$   &$1.24\pm0.01$	 	&$21.90\pm0.17$	&$1.10\pm0.01$	 	&$20.62\pm0.34$	&$1.10\pm0.01$	 	&$18.48\pm0.25$	&$1.17\pm0.01$	 	&$22.96\pm0.18$	&$1.20\pm0.01$   \\
		\hline 
		SSD		   & $14.27\pm0.10$ 	&$1.38\pm0.02$	 	&$16.39\pm0.11$ &$1.38\pm0.02$	 	&$14.27\pm0.21$	&$1.29\pm0.01$	 	&$13.23\pm0.18$	&$1.30\pm0.06$	 	&$12.00\pm0.20$	&$1.26\pm0.01$	 	&$14.58\pm0.11$	&$1.30\pm0.02$	  \\
		\hline 
		CSD inner ring   &  $16.80\pm0.02$	&$1.50\pm0.01$	  &  $18.42\pm0.05$  &$1.60\pm0.04$	 		&$16.29\pm0.29$	&$1.48\pm0.02$	 	&$15.50\pm0.17$	& $1.46\pm0.01$  	&$14.12\pm0.07$	&$1.39\pm0.01$	 	&$16.92\pm0.13$	&$1.50\pm0.01$	  \\
		\hline 
		CSD outer ring            &  $2.16\pm0.02$	&$3.11\pm0.06$	     &$2.26\pm0.02$ &$4.21\pm0.07$	 	&$2.10\pm0.06$	&$3.11\pm0.10$ 	&$1.85\pm0.07$	&$3.24\pm0.06$	 	&$1.80\pm0.10$	&$2.54\pm0.14$	 	&$2.14\pm0.05$	&$3.20\pm0.05$	  	\\
		\hline 
		CSD2			 &  $2.11\pm0.03$	&$3.00\pm0.08$	 			& $2.25\pm0.04$   &$3.69\pm0.16$	 	&$2.24\pm0.05$	&$2.42\pm0.10$	 	&$2.00\pm0.10$	&$2.68\pm0.03$	 	&$1.80\pm0.10$	&$2.55\pm0.20$	 	&$2.19\pm0.12$	&$2.90\pm0.08$	  \\
		\hline 
		CSD9			 &  $0.06\pm0.01$	&$15.16\pm0.10$	 				& $0.15\pm0.04$   & $10.53\pm0.01$	  	&$0.10\pm0.05$	&$5.10\pm0.05$	 	&$0.05\pm0.01$	&$16.40\pm0.10$	  	&$0.09\pm0.07$	&$5.55\pm0.20$	  	&$0.07\pm0.05$	&$14.00\pm0.10$	  \\ 
		\hline
		SSD1		 &  $3.95\pm0.05$	&$1.31\pm0.01$	 	& $4.18\pm0.07$   &$1.59\pm0.08$	 	&$3.95\pm0.13$	&$1.30\pm0.07$	 	&$3.59\pm0.03$	&$1.49\pm0.01$	 	&$3.45\pm0.12$	&$1.40\pm0.08$	 	&$3.91\pm0.06$	&$1.40\pm0.01$  \\
		\hline 
		SSD4		 &  $0.59\pm0.08$	& $9.52\pm0.10$	 		&  $0.57\pm0.09$  &$7.84\pm0.15$	 	&$0.63\pm0.06$	&$4.40\pm0.10$	 	&$1.00\pm0.05$	&$2.51\pm0.16$	 	&$0.60\pm0.80$	&$3.31\pm0.27$	 	&$0.60\pm0.08$	&$5.10\pm0.28$	  \\
		\hline
	\end{tabularx}
	\label{tab:worth}
\end{sidewaystable}

@@

Among the absorbers investigated, the total worth of all CRs extends from $33.7\pm0.4$ $\$$ to $48.19\pm0.68$ 
$\$$ (the first row in Table~\ref{tab:worth}). B$_4$C-90 (boron enriched to 90\% $^{10}$B)
has the largest absorption ability, while Gd$_2$O$_3$ has the lowest 
absorption compared with the other absorbing materials in this study. This 
result agrees with macroscopic absorption cross section data 
\cite{guo2019optimized}. B$_4$C-90 has the highest macroscopic 
absorption cross section followed by Eu$_2$O$_3$, natural B$_4$C (Nat. B$_4$C), HfB$_2$, HfH$_{1.62}$, and 
finally Gd$_2$O$_3$. The CR material is being transmuted during 
operation; the effect of the fuel salt burnup on the CRW is neglected
herein and will be investigated in future work.

@@

We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters (i.e., clusters located in the center and at the boundary between the core
zones, see Figure~\ref{fig:core_25}) to investigate the variation of CRW with the position in the inner core.
The CRW decreases in the direction of the outer core zone. The outer core zone 
has smaller moderator-to-fuel ratio ($0.86$) compared with the central zone 
($2.8$); consequently, the neutron energy spectrum is faster in the peripheral 
zone than in the center of the core degrading the CR's 
absorption ability in that region.

@@

The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner 
ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The 
anti-shadowing is observed when the combined rod worth is greater than the sum 
of the individual worths. As listed in Tables~\ref{tab:worth} and ~\ref{tab:table25}, the strongest anti-shadowing effect occurred in 
SSD4 and CSD9 clusters that are located at the boundary between the core zones 
with different moderator-to-fuel ratios. This can be attributed to the fact that the SSD4 and CSD9 clusters are surrounded by fewer clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~\ref{fig:core_25}). Consequently, low interference between the SSD4 and CSD9 clusters and other surrounding clusters is observed. The obtained results show a negligible relationship between the absorbing material type and the interference between the CR clusters (i.e., the A$_{CRi}$).
